%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% IEEEconf.cls file must exist in the same directory as the TeX file you want to compile
\documentclass[letterpaper, 10 pt, conference]{IEEEconf}

\title{\LARGE \bf
COMPUTER HISTORY\\
\large Group Topic Expressed In A Few Words
}

\author{Group Number\\
\small Group Member 1\\
\small Group Member 2\\
\small Group Member 3\\
}

% Image/graphics support
\usepackage{graphicx}
\graphicspath{ {./images/} }

% Formatting for lists
\usepackage{enumitem}

% Formatting for media
\usepackage{float}
\restylefloat{table}
\restylefloat{figure}

\begin{document}


\maketitle
\thispagestyle{empty}
\pagestyle{empty}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
	Through out history there as been thousands of video games released for computers. Video games are a fun hobby that kills time with ease. Video games are apart of everyday life for some people and very few even make a career just playing video games. If your familiar with famous YouTubers like pewdiepie and markiplier who made millions from Youtube just by playing games that they love then you would know what i'm talking about. When I say this that doesn't mean base all of your career goals on YouTube and video games but it is a possiblility. Computer games have come far in this time from games like Elite Dangerous that has a playing field of a 1 to 1 scale of the entire Milky Way galaxy right on your PC. Games are massive now but where did it all start? 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{TIME PERIOD}

You should describe the time period in which your topic was
invented or used here. Also include the context for why your
topic was created or for how it is used. Any specific historical
information should be included here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{COMPUTER HARDWARE}

You should list the specification of any hardware your topic
uses here. If you want make a table here, please label the table
and include discussion on what components are included in the
table and why. See Table
\ref{tbl:example} for an example of a table.
The labels/captions of the table should be put at the bottom
of the table.


\begin{table}[h!]
\begin{center}
\begin{tabular}{||c | c | c | c||} 
\hline
  & Col1 & Col2 & Col3 \\ [0.5ex]
\hline\hline
Row1 & (1,1) & (1,2) & (1,3) \\ 
\hline
Row2 & (2,1) & (2,2) & (2,3) \\
\hline
Row3 & (3,1) & (3,2) & (3,3) \\
\hline
\end{tabular}
\caption{Example of a table}
\label{tbl:example}
\end{center}
\end{table}

You might want to put figures in the document. Please
remember to label them. The labels/captions of the figures
should be put at the bottom of the figure. See Figure
\ref{fig:example} for an example of how to use figures.
You will need to place the figure in an \texttt{images/} folder
in your working directory.


\section{COMPUTER SOFTWARE}
	There is many softwares that game developers use to help them make the game that they want to make. Game developers use what they call "game engines", "render engines", "physics engines" that provide them with tools and libraries that take care of some of the tedious stuff for them. It basically keeps them from having to re-invent the wheel so to speak. There are many of these game engines that may sound familiar to you like Unity, which is used for high end game development, Physx, and unreal game engine. Amazon actually made a game engine called lumberyard.

\section{CONCLUSION}
	Games have come a very long way from where they started. They went from 2D pixles being ran on a dinosaur machine( I say this not only because the computers were old but also because they were very big! Its like a double metaphore) to 3D graphics with light shading and 3D physics. Games went from bouncing a ball back and fourth on a single screen to the gameplayer being able to explore an entire galaxy. To this, we can conclude that computer games have come a long way from where they started. 

\section*{REFERENCES}

Below are basic formats for different types of references.

\begin{enumerate}[label={[\arabic*]}]
\item Name of Author, ``Title of chapter in the book,''
Title of The Published Book, xth edition. City of
Publisher, Country if not U.S.
\item Name of Author, “Name of paper,” Abbrev.
Title of Periodical, vol. x, no. x, pp. xxx-xxx,
Abbrev. Month, year.
\item Name of Author, (Year, Month),
Title of Internet Article [Online]. Available E-Mail:
E-Mail.
\end{enumerate}

\end{document}

